Title field: summary

### 2021-01-18 inst/examples/title.Rmd
ok

 * `r length(unique(df$title))` [unique titles](output.tables/title_accepted.csv)
 * `r sum(!is.na(df$title))` documents (`r round(100*mean(!is.na(df$title)))`%) have a title
 * [Discarded titles](output.tables/title_discarded.csv)

Top-`r ntop` titles are shown together with the number of documents.

>>>>

 * [Unique accepted titles](output.tables/title_accepted.csv): `r length(unique(df$title))`
 * [Unique discarded titles in original data](output.tables/title_discarded.csv) (excluding NA cases): `r as.vector(countLines(paste0(output.folder, "/title_discarded.csv")) - 1)` 
 * Original documents (`r round(100*mean(!is.na(df$title)), 1)`%) with non-NA titles: `r sum(!is.na(df$title))` / `r nrow(df)`
 * Original documents with missing (NA) titles `r sum(is.na(df$title))` / `r nrow(df)` documents (`r round(100*mean(is.na(df$title)), 1)`%)

Top-`r ntop` titles and their title counts.
